Active Learning for SAT Solver Benchmarking

### 2022-10-10 paper/paper.tex
Revise Section 3.3 (Instance Sampling)
Mostly language, slight change of information-gain formula.

\subsubsection{Static benchmark selection.}

@@

\subsubsection{Algorithm configuration.}

@@

\subsubsection{Incremental benchmark selection.}

@@

\subsubsection{Active learning (AL).}

@@

To be applicable to a new solver $\hat{a}$, whose runtimes are unknown, we extend \emph{score} by replacing $\gamma(a, e)$ with the model's predictions $f : \mathcal{\hat A} \times \mathcal{I} \rightarrow \left\lbrace 1, \dots, k \right\rbrace$.
%JB: "score" and "gamma" aren't defined yet, so there is nothing to extend; score isn't even defined here, only "s", while later sections still use "score"

@@

Selecting an instance based on the model is the core functionality of our method (cf. Algorithm~\ref{algALBenchmark}, Line 2). 
In this section, we introduce our sampling strategies that make use of the model's label-prediction function $f$ which are inspired by existing work within the realms of active learning~\cite{settles2009active}.
We implement a model-uncertainty based approach and a model-based information-gain sampling strategy.
These methods require the model's predictions to also include probabilities for the $k$ possible runtime labels denoted by $f' : \mathcal{\hat A} \times \mathcal{I} \rightarrow \left[0, 1\right]^k$.

\subsubsection{Model Uncertainty Based Sampling.}

The model-uncertainty-based approach simply selects the instance that is closest to the model's decision boundary.

\begin{equation*}
  \underset{e \in \mathcal{I} \setminus \tilde{\mathcal{I}}}{\arg\min} \left\lvert \frac{1}{k} - \max_{n \in \left\lbrace 1, \dots, k \right\rbrace} f'\!\left(\hat{a}, e\right)_{n} \right\rvert
\end{equation*}

\subsubsection{Information Gain Based Sampling.}

The model-based information-gain sampling strategy selects the instance with the highest expected entropy reduction.
To be more specific, we select the instance $e$ that maximizes $IG(e)$ which is specified as follows.

\begin{equation*}
  \operatorname{IG}(e) := \operatorname{H}(e) - \sum_{n = 1}^{k} f'(\hat{a}, e)_{n} \operatorname{H}(e, n)
\end{equation*}

Here $\operatorname{H}(e)$ denotes the entropy of the runtime labels $\gamma(a, e)$ for all $a \in \mathcal{A}$ and $\operatorname{H}(e, n)$ denotes the entropy of the runtime labels including the runtime label of $\hat{a}$ which is $n$.
The term $\operatorname{H}(e, n)$ is computed for every possible runtime label $n \in \{1, \dots, k\}$.

%JB: if this is info gain regarding runtimes, doesn't Eq. (4) mean that we would prefer instances with low entropy of runtime distribution after considering the new solver, i.e., instances that are not very discriminatory?
%TF: I don't think so. We want to maximize the reduction in entropy of the runtime labels. Low entropy afterward -> we know that the solver behaves similarly to existing ones.

@@

%Bossek and Wagner~\cite{Bossek021a} introduce a custom ranking-score metric incorporating the number of \emph{good} pairs and \emph{bad} pairs.
%JB: some selection methods, like this one, are not mentioned later anymore (in particular, not in experimental design), so we don't need to describe them in detail (maybe mention them shortly if used in preliminary experiments, but turned out to be not useful)
%TF: I've cut the section down a bit
%A good solver pair, regarding a particular instance, are solvers that perform according to their global ranking.
%Otherwise, it is a \emph{bad} pair.
%Based on this classification, they assign a custom score to each instance.
%By selecting instances with the highest score, they try to favor instances that are predictive of the final ranking.

>>>>

\subsubsection{Static Benchmark Selection.}

@@

\subsubsection{Algorithm Configuration.}

@@

\subsubsection{Incremental Benchmark Selection.}

@@

\subsubsection{Active Learning (AL).}

@@

To be applicable to a new solver $\hat{a}$, whose runtimes are unknown, we extend \emph{score} by replacing $\gamma(a, e)$ with the model's predictions $f : \mathcal{\hat A} \times \mathcal{I} \rightarrow \left\lbrace 1, \dots, k \right\rbrace$.
%JB: "score" and "gamma" aren't defined yet, so there is nothing to extend; score isn't even defined here, only "s", while later sections still use "score"
%JB: also, each model only predicts for one solver (there is no model covering multiple solvers), so I'm not sure whether introducing the solver as parameter makes sense

@@

Selecting an instance based on the model is a core functionality of our framework (cf. Algorithm~\ref{algALBenchmark}, Line 2).
In this section, we introduce our sampling strategies, which make use of the model's label-prediction function $f$ and are inspired by existing work within the realms of active learning~\cite{settles2009active}.
We implement a model-uncertainty and an information-gain sampling strategy.
These methods require the model's predictions to also include probabilities for the $k$ possible runtime labels.
Let $f' : \mathcal{\hat A} \times \mathcal{I} \rightarrow \left[0, 1\right]^k$ denote this modified prediction function.

\subsubsection{Model Uncertainty Sampling.}

The model-uncertainty sampling strategy simply selects the instance that is closest to the model's decision boundary.

\begin{equation*}
  \underset{e \in \mathcal{I} \setminus \tilde{\mathcal{I}}}{\arg\min} \left\lvert \frac{1}{k} - \max_{n \in \left\lbrace 1, \dots, k \right\rbrace} f'\!\left(\hat{a}, e\right)_{n} \right\rvert
  %JB: \tilde I is undefined
\end{equation*}

\subsubsection{Information Gain Sampling.}

The information-gain sampling strategy selects the instance with the highest expected entropy reduction regarding the runtime labels of the instance.
To be more specific, we select the instance $e$ that maximizes $IG(e)$, which is specified as follows:

\begin{equation*}
  \operatorname{IG}(e) := \operatorname{H}(e) - \sum_{n = 1}^{k} f'(\hat{a}, e)_{n} \operatorname{\hat H}_n(e)
\end{equation*}

Here, $\operatorname{H}(e)$ denotes the entropy of the runtime labels $\gamma(a, e)$ over all $a \in \mathcal{A}$ and $\operatorname{H}(e, n)$ denotes the entropy of these labels plus $n$ as the runtime label for $\hat{a}$.
The term $\operatorname{\hat H}_n(e)$ is computed for every possible runtime label $n \in \{1, \dots, k\}$.

%JB: if this is info gain regarding runtimes, doesn't Eq. (4) mean that we would prefer instances with low entropy of runtime distribution after considering the new solver, i.e., instances that are not very discriminatory?
%TF: I don't think so. We want to maximize the reduction in entropy of the runtime labels. Low entropy afterward -> we know that the solver behaves similarly to existing ones.
%JB: but if we want to discriminate between solvers, what does it help to know that solver behaves similarly to other solvers?

@@

%Bossek and Wagner~\cite{Bossek021a} introduce a custom ranking-score metric incorporating the number of \emph{good} pairs and \emph{bad} pairs.
%A good solver pair, regarding a particular instance, are solvers that perform according to their global ranking.
%Otherwise, it is a \emph{bad} pair.
%Based on this classification, they assign a custom score to each instance.
%By selecting instances with the highest score, they try to favor instances that are predictive of the final ranking.
